Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-19 reanalysis-3-propensity_scores.qmd
\n remove

for (i in 1:n_imputations) {
  cat("Processing imputation", i, "of", n_imputations, "...\n")

@@

  cat("  - Trees used (es.mean):", twang_model$desc$es.mean$n.trees, "\n")
  cat("  - Weight range: [", round(min(weights), 3), ",", round(max(weights), 3), "]\n")
}

cat("\nTwang propensity score calculation complete\n")
```

@@

  if (i <= max_imputations_for_diagnostics) {
    cat("\nBalance summary for imputation", i, ":\n")
    print(summary(twang_model))
  }
}

@@

cat("\nGenerating twang diagnostic plots for", n_to_show, "imputations...\n")

# For each selected imputation, show twang-specific diagnostics
for (i in imps_to_show) {
  cat("\nDiagnostics for Imputation", i, ":\n")

@@

  tryCatch({
    plot(twang_model)
  }, error = function(e) {
    cat("  Standard plots not available, generating custom diagnostics...\n")

@@

# Plot PS distribution for first few imputations
for (i in imps_to_show) {
  cat("\nPropensity score distributions for imputation", i, "\n")

@@

  cat("  Weight summary:\n")
  cat("    Control: mean =", round(mean(weights[!treated]), 3), 
      ", max =", round(max(weights[!treated]), 3), "\n")
  cat("    Treated: mean =", round(mean(weights[treated]), 3),
      "(should be 1.0 for ATT)\n")
}
```

>>>>

for (i in 1:n_imputations) {
  cat("Processing imputation", i, "of", n_imputations, "...")

@@

  cat("  - Trees used (es.mean):", twang_model$desc$es.mean$n.trees, "")
  cat("  - Weight range: [", round(min(weights), 3), ",", round(max(weights), 3), "]")
}

cat("Twang propensity score calculation complete")
```

@@

  if (i <= max_imputations_for_diagnostics) {
    cat("Balance summary for imputation", i)
    print(summary(twang_model))
  }
}

@@

cat("Generating twang diagnostic plots for", n_to_show, "imputations...")

# For each selected imputation, show twang-specific diagnostics
for (i in imps_to_show) {
  cat("Diagnostics for Imputation", i, ":")

@@

  tryCatch({
    plot(twang_model)
  }, error = function(e) {
    cat("  Standard plots not available, generating custom diagnostics...")

@@

# Plot PS distribution for first few imputations
for (i in imps_to_show) {
  cat("Propensity score distributions for imputation", i, "")

@@

  cat("  Weight summary:")
  cat("    Control: mean =", round(mean(weights[!treated]), 3), 
      ", max =", round(max(weights[!treated]), 3), "")
  cat("    Treated: mean =", round(mean(weights[treated]), 3),
      "(should be 1.0 for ATT)")
}
```
